### 2021-08-10 paper/paper.tex
More changes to section 3

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. To make the mesh curvilinear, the interior of the box is heavily warped
by a combination of sine and cosine functions~\cite{chan2019efficient}. To integrate up to the
final time $t=1.0$, both codes use the five-stage, four-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

@@

For these comparisons we examine the performance of FLUXO and \trixi for the weak
form as well as flux differencing implementations of the DG solver. For the weak form simulations we compute
the coupling between elements with a Harten-Lax-van Leer (HLL) numerical surface flux function~\cite{Toro2009,li2005hllc}.
For the flux differencing solver, which introduces an additional numerical volume flux function, we use an entropy-conservative flux
function in both the volume and at the surface. For the compressible Euler equations
this flux is also kinetic energy preserving~\cite{ranocha2020icosahom, ranocha2018thesis}
while for the ideal MHD equations it is kinetic and magnetic energy preserving~\cite{hindenlang2019}. We note that both ideal MHD implementations
contain additional computational overhead due to nonconservative terms necessary for the numerical approximation
to remain entropy consistent~\cite{bohm2020}. Additionally, the weak form DG solver type is recovered if one uses a central flux
in the volume of the flux differencing DG solver, albeit with additional computational cost~\cite{gassner2016split}.

All simulations for the performance comparison were run on the HPC system Tetralith
provided by the Swedish National Infrastructure for Computing (SNIC).
Each node of Tetralith has two sockets, each with an Intel(R) Xeon(R) Gold 6130 @ 2.10GHz with 96GiB of memory.
FLUXO was compiled using the Intel compiler suite v18.0.3 and \trixi used Julia v1.6.1.
The serial performance results were run on a single core.
We ran each configuration of a particular physical setup, polynomial degree, and solver type
for each code five times, taking the smallest value from each in the comparison results.

To assess the performance of the two codes we vary the polynomial degree
(\lstinline{polydeg}) in the range $[3,15]$.
This corresponds to considering DG approximations of (increasing) spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock-time}}{\#\text{time steps}\cdot 5\cdot\#\text{elements}\cdot(\text{\lstinline{polydeg}}+1)^3},
\end{equation}
where $5$ is the number of RK stages per time step for the selected time-stepping method. In other words, the PID acts 
as a metric for the run time required for the right hand side (RHS) evaluation of each DOF.

The code and detailed information necessary to reproduce these numerical
experiments is available in the accompanying repository \cite{ranocha2021adaptiveRepro}.

@@

The results of these performance comparisons are visualized for the 3D compressible Euler
in Figure~\ref{fig:PID-Euler} and for the 3D ideal MHD equations in Figure~\ref{fig:PID-MHD}.
We present the PID timings for both codes in the top portion of these two figures as well as
a relative comparison using FLUXO as reference. Therefore, smaller values in the bottom portion
the Figures~\ref{fig:PID-Euler} and \ref{fig:PID-MHD} are better.

@@

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the version compiled using Intel was between \SI{5}{\percent} to \SI{23}{\percent} faster.
Thus, only results from the Intel compiler are included.
It is also possible to see the additional computational overhead for the entropy conservative, flux
differencing DG methods for both physical models. This is because the numerical fluxes are more complex, in
terms of computational effort, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.

>>>>

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. To make the mesh curvilinear, the interior of the box is heavily warped
by a combination of sine and cosine functions~\cite{chan2019efficient}. To integrate up to the
final time $t=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

@@

For these comparisons we examine the performance of FLUXO and \trixi for the weak
form as well as flux differencing implementations of the DG solver. For the weak form simulations we compute
the coupling between elements with a Harten-Lax-van Leer (HLL) numerical surface flux function~\cite{Toro2009,li2005hllc}.
For the flux differencing solver, which introduces an additional numerical volume flux function, we use an entropy-conservative flux
function in both the volume and at the surface. For the compressible Euler equations
this flux is also kinetic energy preserving~\cite{ranocha2020icosahom, ranocha2018thesis}
while for the ideal MHD equations it is kinetic and magnetic energy preserving~\cite{hindenlang2019}. We note that both ideal MHD implementations
require additional computational effort due to nonconservative terms necessary for the numerical approximation
to remain entropy consistent~\cite{bohm2020}. Additionally, the weak form DG solver type is recovered if one uses a central flux
in the volume of the flux differencing DG solver, albeit with additional computational cost~\cite{gassner2016split}.

All simulations for the performance comparison were run on the HPC system Tetralith
provided by the Swedish National Infrastructure for Computing (SNIC).
Each node of Tetralith has two sockets, each with an Intel(R) Xeon(R) Gold 6130 @ 2.10GHz with 96GiB of memory.
FLUXO was compiled using the Intel compiler suite v18.0.3 and \trixi used Julia v1.6.1.
The serial performance results were run on a single core.
We ran each configuration of a particular physical setup, polynomial degree, and solver type
for each code five times, taking the smallest value from each for the comparison results.

To assess the performance of the two codes, we vary the polynomial degree
(\lstinline{polydeg}) in the range $[3,15]$.
This corresponds to considering DG approximations of (increasing) spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock time}}{\#\text{time steps}\cdot 5\cdot\#\text{elements}\cdot(\text{\lstinline{polydeg}}+1)^3},
\end{equation}
where $5$ is the number of Runge-Kutta stages per time step for the selected time-stepping method. In other words, the PID acts
as a metric for the run time required for the right hand side (RHS) evaluation of each DOF.

The code and detailed information necessary to reproduce these numerical
experiments are available in the accompanying repository \cite{ranocha2021adaptiveRepro}.

@@

The results of these performance measurements are visualized for the 3D compressible Euler equations
in Figure~\ref{fig:PID-Euler} and for the 3D ideal MHD equations in Figure~\ref{fig:PID-MHD}.
We present the absolute PID timings for both codes in the top portion of these two figures and 
a relative comparison using FLUXO as reference in the bottom portion; smaller values thus are always
better.

@@

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the version compiled using Intel was between \SI{5}{\percent} to \SI{23}{\percent} faster.
Thus, only results from the Intel compiler are included.
It is also possible to see the additional computational effort for the entropy-conservative flux
differencing DG methods for both physical systems. This is because the numerical fluxes are more
expensive in
terms of computational cost, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.
